DATA 621 - Business Analytics and Data Mining

### 2020-11-20 HW5/HW5-Draft.Rmd
Missing data. Clean up loads until needed

```{r loadData, include=FALSE}
# Load necessary libraries
library(arm)
library(dplyr)
library(ggplot2)
library(scales)
library(knitr)
library(caret)
library(RANN)
library(pROC)
library(mice)
library(corrplot)
library(data.table)

@@

# Number of training observations
ntrobs <- dim(DT)[[1]]

@@

There are `r ntrobs` observations. All of these predictors are numeric, although
some `LabelAppeal` and `STARS` could be considered ordered factors. There are a
lot of missing values for some of the predictors.

```{r missing}
Missing <- t(DT[, lapply(.SD, function(x) {sum(is.na(x))}),
                .SDcols = -c('INDEX', 'TARGET')])
kable(Missing, col.names = 'Missing',
      caption = 'Predictors with Missing Observations')
```

>>>>

```{r loadData, include=FALSE}
# Load necessary libraries
library(ggplot2)
library(scales)
library(knitr)
library(caret)
library(corrplot)
library(data.table)

@@

# Number of training observations
ntrnobs <- dim(DT)[[1]]

@@

There are `r ntrnobs` observations. All of these predictors are numeric,
although some `LabelAppeal` and `STARS` could be considered ordered factors. For
the purposes of this assignment, it makes sense to treat every predictor as
numeric.

## Missing Data
There are a lot of missing values for some of the predictors.

```{r missing}
missingPreds <- transpose(DT[, lapply(.SD, function(x) {sum(is.na(x))}),
                             .SDcols = -c('INDEX', 'TARGET')],
                          keep.names = 'Predictors')
setnames(missingPreds, 'V1', 'Missing')
missingPreds[, Percentage := Missing / ntrnobs * 100]
setorder(missingPreds, -Missing)
kable(missingPreds, digits = 2L, caption = 'Predictors with Missing Observations')
```

`STARS` is especially sparse, but as noted in the assignment, this may be an
indication in and of its own. It is reasonable to assume that the vinters of a
good wine want it to be rated. If they do not submit it for rating, that may be
an indication of their lack of faith in the wine. How to factor this into the
analysis will be decided individually by the modelers in this assignment. The
other missing variables are all less than 10%, and their handling via imputation
or otherwise will be done on a model-by-model basis as well.
